---
title: "Cameroon Height Comparisons"
output:
  html_notebook: default
  word_document: default
  pdf_document: default
---

#### This notebook contains:
* 
* 
* 
* 

#### Default, Algorithm 3, and Algorithm 2 Comparisons Between GEDI and CHM data

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
library(rgdal)
library(tidyverse)
library(skimr)
library(stringr)
library(readxl)
library(raster)
library(Metrics)
library(hydroGOF)
library(SimDesign)
library(rgeos)
library(ggspatial)
plotdat <- read.csv( "~/Desktop/Research_2022/Data/GEDI/cam_field_gedi_lidar.csv")

summary(plotdat)
class(plotdat$rh100)
# r squared calculation
rsq <-  function(x, y) summary(lm(y~x))$r.squared
```

```{r}
# Multiple plot function
# http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


## Default Algorithm 
```{r}
# Calculate R squared and RMSE 
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85,plotdat$height85), digits = 4)

RMSE80 <-round(hydroGOF::rmse(plotdat$rh80,plotdat$height80), digits = 4)
r2_80 <- round(rsq(plotdat$rh80,plotdat$height80), digits = 4)
pear_cor_80 <- cor(plotdat$rh80,plotdat$height80, method = "pearson")
spear_cor_80 <- cor(plotdat$rh80,plotdat$height80, method = "spearman")
pear_cor_80_test <- cor.test(plotdat$rh80,plotdat$height80, method = "pearson")
spear_cor_80_test <- cor.test(plotdat$rh80,plotdat$height80, method = "spearman")
bias80 <-round(bias(plotdat$rh80,plotdat$height80), digits = 4)

RMSE75 <-round(hydroGOF::rmse(plotdat$rh75,plotdat$height75), digits = 4)
r2_75 <- round(rsq(plotdat$rh75,plotdat$height75), digits = 4)
pear_cor_75 <- cor(plotdat$rh75,plotdat$height75, method = "pearson")
spear_cor_75 <- cor(plotdat$rh75,plotdat$height75, method = "spearman")
pear_cor_75_test <- cor.test(plotdat$rh75,plotdat$height75, method = "pearson")
spear_cor_75_test <- cor.test(plotdat$rh75,plotdat$height75, method = "spearman")
bias75 <-round(bias(plotdat$rh75,plotdat$height75), digits = 4)

RMSE70 <-round(hydroGOF::rmse(plotdat$rh70,plotdat$height70), digits = 4)
r2_70 <- round(rsq(plotdat$rh70,plotdat$height70), digits = 4)
pear_cor_70 <- cor(plotdat$rh70,plotdat$height70, method = "pearson")
spear_cor_70 <- cor(plotdat$rh70,plotdat$height70, method = "spearman")
pear_cor_70_test <- cor.test(plotdat$rh70,plotdat$height70, method = "pearson")
spear_cor_70_test <- cor.test(plotdat$rh70,plotdat$height70, method = "spearman")
bias70 <-round(bias(plotdat$rh70,plotdat$height70), digits = 4)

RMSE65 <-round(hydroGOF::rmse(plotdat$rh65,plotdat$height65), digits = 4)
r2_65 <- round(rsq(plotdat$rh65,plotdat$height65), digits = 4)
pear_cor_65 <- cor(plotdat$rh65,plotdat$height65, method = "pearson")
spear_cor_65 <- cor(plotdat$rh65,plotdat$height65, method = "spearman")
pear_cor_65_test <- cor.test(plotdat$rh65,plotdat$height65, method = "pearson")
spear_cor_65_test <- cor.test(plotdat$rh65,plotdat$height65, method = "spearman")
bias65 <-round(bias(plotdat$rh65,plotdat$height65), digits = 4)

# 80/75 are best (r2 same)

# put rh95 as a point of comparison
# there is a bias in the measurements 
## what argument can you formulate from why
## any other information or analyses you can do 
## can do reading about it
## not noise, introduces scatter, not bias
## not ground a

```

```{r,}
par(mfrow=c(2,1))
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```



```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_default, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_default, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_default, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_default, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```

## Algorithm 2

```{r}
# Calculate R squared and RMSE 
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_a2,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_a2,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_a2,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_a2,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_a2,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_a2,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_a2,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_a2,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_a2,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_a2,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_a2,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_a2,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_a2,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_a2,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_a2,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_a2,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_a2,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_a2,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_a2,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_a2,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_a2,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_a2,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_a2,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_a2,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_a2,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_a2,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_a2,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_a2,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_a2,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_a2,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_a2,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_a2,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_a2,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_a2,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_a2,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_a2,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_a2,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_a2,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_a2,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_a2,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_a2,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_a2,plotdat$height85), digits = 4)

pear_cor_85
spear_cor_85
pear_cor_85_test 
spear_cor_85_test
```

```{r,}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```


```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a2, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a2, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a2, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a2, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
## Algorithm 3

```{r}
# Calculate R squared and RMSE 
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_a3,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_a3,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_a3,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_a3,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_a3,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_a3,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_a3,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_a3,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_a3,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_a3,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_a3,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_a3,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_a3,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_a3,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_a3,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_a3,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_a3,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_a3,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_a3,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_a3,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_a3,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_a3,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_a3,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_a3,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_a3,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_a3,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_a3,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_a3,plotdat$height95), digits = 4)
```

```{r,}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a3, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a3, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a3, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a3, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
Comparison of Copernicus and drone lidar elevation
```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$coper_elev, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$coper_elev, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$coper_elev, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$coper_elev, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
```

```{r}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,coper_elev), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```

Height comparisons with copernicus elevation adjustment

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust <- plotdat$Elevation-plotdat$coper_elev
summary(plotdat$elev_adjust)

plotdat$rh100_adj <- plotdat$rh100 + plotdat$elev_adjust
summary(plotdat$rh100_adj)
plotdat$rh99_adj <- plotdat$rh99 + plotdat$elev_adjust
summary(plotdat$rh99_adj)
plotdat$rh98_adj <- plotdat$rh98 + plotdat$elev_adjust
summary(plotdat$rh98_adj)
plotdat$rh95_adj <- plotdat$rh95 + plotdat$elev_adjust
summary(plotdat$rh95_adj)
plotdat$rh90_adj <- plotdat$rh90 + plotdat$elev_adjust
summary(plotdat$rh90_adj)
plotdat$rh85_adj <- plotdat$rh85 + plotdat$elev_adjust
summary(plotdat$rh85_adj)
```
```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

Height comparisons with elevation adjustment

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust <- plotdat$Elevation-plotdat$lidar_elev
summary(plotdat$elev_adjust)

plotdat$rh100_adj <- plotdat$rh100 + plotdat$elev_adjust
summary(plotdat$rh100_adj)
plotdat$rh99_adj <- plotdat$rh99 + plotdat$elev_adjust
summary(plotdat$rh99_adj)
plotdat$rh98_adj <- plotdat$rh98 + plotdat$elev_adjust
summary(plotdat$rh98_adj)
plotdat$rh95_adj <- plotdat$rh95 + plotdat$elev_adjust
summary(plotdat$rh95_adj)
plotdat$rh90_adj <- plotdat$rh90 + plotdat$elev_adjust
summary(plotdat$rh90_adj)
plotdat$rh85_adj <- plotdat$rh85 + plotdat$elev_adjust
summary(plotdat$rh85_adj)
```

```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust_default <- plotdat$Elevation_default-plotdat$lidar_elev
summary(plotdat$elev_adjust_default)

plotdat$rh100_adj_default <- plotdat$rh100 + plotdat$elev_adjust_default
summary(plotdat$rh100_adj_default)
plotdat$rh99_adj_default <- plotdat$rh99 + plotdat$elev_adjust_default
summary(plotdat$rh99_adj_default)
plotdat$rh98_adj_default <- plotdat$rh98 + plotdat$elev_adjust_default
summary(plotdat$rh98_adj_default)
plotdat$rh95_adj_default <- plotdat$rh95 + plotdat$elev_adjust_default
summary(plotdat$rh95_adj_default)
plotdat$rh90_adj_default <- plotdat$rh90 + plotdat$elev_adjust_default
summary(plotdat$rh90_adj_default)
plotdat$rh85_adj_default <- plotdat$rh85 + plotdat$elev_adjust_default
summary(plotdat$rh85_adj_default)
```
```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj_default,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj_default,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj_default,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj_default,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj_default,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj_default,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj_default,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj_default,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj_default,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj_default,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj_default,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj_default,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj_default,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj_default,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj_default,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj_default,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj_default,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj_default,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj_default,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj_default,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj_default,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj_default,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj_default,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj_default,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj_default,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj_default,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj_default,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj_default,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj_default,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj_default,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj_default,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj_default,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj_default,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj_default,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj_default,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj_default,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj_default,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj_default,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj_default,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```



### Comparisons between CHM and Ground Data
```{r, echo=FALSE}
grounddat_field_gedi <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_gedi_field.csv")
grounddat_field_gedi <- na.omit(grounddat_field_gedi)
grounddat_lidar <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_field_lidar.csv")

str(grounddat_field_gedi$field_height100)
```



```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)
r2_100 <- round(rsq(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)
pear_cor_100 <- cor(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "pearson")
spear_cor_100 <- cor(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "spearman")
bias100 <- round(bias(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)
r2_99 <- round(rsq(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)
pear_cor_99 <- cor(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "pearson")
spear_cor_99 <- cor(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "spearman")
bias99 <-round(bias(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)
r2_98 <- round(rsq(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)
pear_cor_98 <- cor(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "pearson")
spear_cor_98 <- cor(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "spearman")
bias98 <-round(bias(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)
r2_95 <- round(rsq(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)
pear_cor_95 <- cor(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "pearson")
spear_cor_95 <- cor(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "spearman")
bias95 <-round(bias(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height100,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height99,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height98,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height95,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

### Comparison between Ground and Gedi
## Default
```{r,}
grounddat_field_gedi %>%
  ggplot() + 
  geom_point(mapping = aes(rh100,field_height), col = "blue")+
  geom_abline(intercept = 0, slope = 1)
grounddat_field_gedi %>%
  ggplot() + 
  geom_point(mapping = aes(rh98,field_height), col = "blue")+
  geom_abline(intercept = 0, slope = 1)
```

```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

## Alg 2
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100_a2,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99_a2,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98_a2,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95_a2,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

## Alg 3
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100_a3,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99_a3,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98_a3,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95_a3,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```









Fancy Plot

```{r}
# gedi
dat <- read_csv("~/Desktop/Research_2022/Data/GEDI/cameroon_filtered_with_distances.csv")
# Read in field data
fielddat <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_field_lidar.csv")
# reserve- for crs
reserve <- readOGR('~/Desktop/Research/Cameroon/DjaFaunalReserve',"DjaFaunalReserveOSM")
# Cameroon lidar
cam_lidar <- raster("~/Desktop/Research/Cameroon/CHM_1m.tif")

# make list of shots
shot <- as.list(unique(fielddat$Shot_Number))
dat <- dat[dat$Shot_Number%in% shot, ]
shot <- as.list(unique(dat$Shot_Number))


# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs"))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)
plot(cam_buff)

hei <- as(cam_buff, "data.frame")
chm <- raster::extract(cam_lidar, cam_buff, method = "simple", df=TRUE, cellnumbers=TRUE)
summary(hei$lidar_height)
```

```{r}
# make fancy plot
i = 1
par(mfrow = c(3,5), mai=c(0,0,0,0))
for (val in shot){
  temp <- subset(dat, dat$Shot_Number == val)
  # convert GEDI data to spatial points dataframe
  cam_proj <- crs(reserve)
  coords<- temp[,c("Longitude","Latitude")]
  temp_spdf <- SpatialPointsDataFrame(coords=coords,
                                     data=temp,
                                     proj4string=cam_proj)
  temp_spdf <- spTransform(temp_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
  temp_buff <- gBuffer(temp_spdf, width= 42, byid = TRUE)
  lidar_chm_crop <- cam_lidar %>% mask(temp_buff) %>%
          crop(temp_buff)
  plot(lidar_chm_crop, 
     breaks = c(5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60), 
     col = terrain.colors(12), legend = FALSE, ylab="",yaxt="n", xlab="",xaxt="n")
  i = i+1}
plot(lidar_chm_crop, legend.only = TRUE, cex = 2)
```


```{r}
# Fancy plots
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")

# make field data into shp file
field <- subset(fielddat, fielddat$Shot_Number == "s29010100300314279")
coords<- field[,c("Longitude","Latitude")]
cam_proj <- crs(reserve)
spdf_ground <- SpatialPointsDataFrame(coords=coords,
                                   data=field,
                                   proj4string=cam_proj)
spdf_ground <- spTransform(spdf_ground, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# subset really tall tree
#tall <- subset(fielddat, fielddat$`Tree ID` == 68)
#coords<- tall[,c("Longitude","Latitude")]
#cam_proj <- crs(reserve)
#tall_spdf <- SpatialPointsDataFrame(coords=coords,
#                                   data=tall,
#                                   proj4string=cam_proj)
#tall_spdf <- spTransform(tall_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# add shapefile on top of the existing raster
plot(lidar_chm_crop)
plot(spdf_ground, add = TRUE, col = spdf_ground$Height)
plot(tall_spdf, add = TRUE, col = "white")
summary(lidar_chm_crop)
```

```{r}
# Fancy plots
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")
```

```{r}
# Make a function that creates plot when given a shot number
make_plot <- function(shot_num) {
  dat <- subset(dat, dat$Shot_Number == shot_num)
  # convert GEDI data to spatial points dataframe
  cam_proj <- crs(reserve)
  coords<- dat[,c("Longitude","Latitude")]
  cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                     data=dat,
                                     proj4string=cam_proj)
  cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
  cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)
  lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
            crop(cam_buff)
  p1<-plot(lidar_chm_crop, 
     breaks = c(10, 20, 30, 40, 50), 
     col = terrain.colors(5), legend = FALSE)
}

plot(lidar_chm_crop, 
     breaks = c(5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60), 
     col = terrain.colors(12))
```

```{r}
par(mfrow=c(3,1))
make_plot("s29010100300314279")
make_plot("s29010100300314279")
plot(lidar_chm_crop, legend.only=TRUE)
```



```{r}
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")
```


```{r}
dat <- subset(dat, dat$Shot_Number == "s29010000300321833")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop)
p1 <- plot(lidar_chm_crop, xlim = c(257097, 257099),
     ylim = c(353060, 353080), main = "Cropped lidar chm")

# make field data into shp file
field <- subset(fielddat, fielddat$Shot_Number == "s29010000300321833")
coords<- field[,c("Longitude","Latitude")]
cam_proj <- crs(reserve)
spdf_ground <- SpatialPointsDataFrame(coords=coords,
                                   data=field,
                                   proj4string=cam_proj)
spdf_ground <- spTransform(spdf_ground, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# add shapefile on top of the existing raster
plot(lidar_chm_crop)
plot(spdf_ground, add = TRUE, col = spdf_ground$Height)
plot(tall_spdf, add = TRUE, col = "white")
summary(lidar_chm_crop)
```
## Summary of Results
\begin{tabular}{|c|c|c|}
		\multicolumn{1}{r}{}
		&  \multicolumn{1}{c}{Cancer}
		& \multicolumn{1}{c}{No cancer}
		& \multicolumn{1}{c}{Total} \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
\end{tabular}


