---
title: "Cameroon Height Comparisons"
output:
  pdf_document: default
  word_document: default
  html_notebook: default
---

#### This notebook contains:
* 
* 
* 
* 

#### Default, Algorithm 3, and Algorithm 2 Comparisons Between GEDI and CHM data

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
library(rgdal)
library(tidyverse)
library(skimr)
library(stringr)
library(readxl)
library(raster)
library(Metrics)
library(hydroGOF)
library(SimDesign)
library(rgeos)
library(ggspatial)
library(gridExtra)
plotdat <- read.csv("~/Desktop/Research_2022/Data/GEDI/cam_field_gedi_lidar_all.csv")

coverage <- subset(plotdat, Beam == "BEAM0000" | Beam == "BEAM0001" | Beam == "BEAM0010" | Beam == "BEAM0011")
fullpower <- subset(plotdat, Beam == "BEAM0101" | Beam == "BEAM0110" | Beam == "BEAM1000" |  Beam == "BEAM1011")
# r squared calculation
rsq <-  function(x, y) summary(lm(y~x))$r.squared
```

```{r}
# Multiple plot function
# http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2)/
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```



#----------------------------------------------#
#----------------------------------------------#
##------------- Default Algorithm--------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE100_default <- round(hydroGOF::rmse(coverage$rh100,coverage$height100), digits = 4)
r2_100_default <- round(rsq(coverage$rh100,coverage$height100), digits = 4)
pear_cor_100_default <- cor(coverage$rh100,coverage$height100, method = "pearson")
spear_cor_100_default <- cor(coverage$rh100,coverage$height100, method = "spearman")
pear_cor_100_test_default <- cor.test(coverage$rh100,coverage$height100, method = "pearson")
spear_cor_100_test_default <- cor.test(coverage$rh100,coverage$height100, method = "spearman")
bias100_default <- round(bias(coverage$rh100,coverage$height100), digits = 4)

RMSE99_default <-round(hydroGOF::rmse(coverage$rh99,coverage$height99), digits = 4)
r2_99_default <- round(rsq(coverage$rh99,coverage$height99), digits = 4)
pear_cor_99_default <- cor(coverage$rh99,coverage$height99, method = "pearson")
spear_cor_99_default <- cor(coverage$rh99,coverage$height99, method = "spearman")
pear_cor_99_test_default <- cor.test(coverage$rh99,coverage$height99, method = "pearson")
spear_cor_99_test_default <- cor.test(coverage$rh99,coverage$height99, method = "spearman")
bias99_default <-round(bias(coverage$rh99,coverage$height99), digits = 4)

RMSE98_default <-round(hydroGOF::rmse(coverage$rh98,coverage$height98), digits = 4)
r2_98_default <- round(rsq(coverage$rh98,coverage$height98), digits = 4)
pear_cor_98_default <- cor(coverage$rh98,coverage$height98, method = "pearson")
spear_cor_98_default <- cor(coverage$rh98,coverage$height98, method = "spearman")
pear_cor_98_test_default <- cor.test(coverage$rh98,coverage$height98, method = "pearson")
spear_cor_98_test_default <- cor.test(coverage$rh98,coverage$height98, method = "spearman")
bias98_default <-round(bias(coverage$rh98,coverage$height98), digits = 4)

RMSE95_default <-round(hydroGOF::rmse(coverage$rh95,coverage$height95), digits = 4)
r2_95_default <- round(rsq(coverage$rh95,coverage$height95), digits = 4)
pear_cor_95_default <- cor(coverage$rh95,coverage$height95, method = "pearson")
spear_cor_95_default <- cor(coverage$rh95,coverage$height95, method = "spearman")
pear_cor_95_test_default <- cor.test(coverage$rh95,coverage$height95, method = "pearson")
spear_cor_95_test_default <- cor.test(coverage$rh95,coverage$height95, method = "spearman")
bias95_default <-round(bias(coverage$rh95,coverage$height95), digits = 4)

RMSE90_default <-round(hydroGOF::rmse(coverage$rh90,coverage$height90), digits = 4)
r2_90_default <- round(rsq(coverage$rh90,coverage$height90), digits = 4)
pear_cor_90_default <- cor(coverage$rh90,coverage$height90, method = "pearson")
spear_cor_90_default <- cor(coverage$rh90,coverage$height90, method = "spearman")
pear_cor_90_test_default <- cor.test(coverage$rh90,coverage$height90, method = "pearson")
spear_cor_90_test_default <- cor.test(coverage$rh90,coverage$height90, method = "spearman")
bias90_default <-round(bias(coverage$rh90,coverage$height90), digits = 4)

RMSE85_default <-round(hydroGOF::rmse(coverage$rh85,coverage$height85), digits = 4)
r2_85_default <- round(rsq(coverage$rh85,coverage$height85), digits = 4)
pear_cor_85_default <- cor(coverage$rh85,coverage$height85, method = "pearson")
spear_cor_85_default <- cor(coverage$rh85,coverage$height85, method = "spearman")
pear_cor_85_test_default <- cor.test(coverage$rh85,coverage$height85, method = "pearson")
spear_cor_85_test_default <- cor.test(coverage$rh85,coverage$height85, method = "spearman")
bias85_default <-round(bias(coverage$rh85,coverage$height85), digits = 4)

RMSE80_default <-round(hydroGOF::rmse(coverage$rh80,coverage$height80), digits = 4)
r2_80_default <- round(rsq(coverage$rh80,coverage$height80), digits = 4)
pear_cor_80_default <- cor(coverage$rh80,coverage$height80, method = "pearson")
spear_cor_80_default <- cor(coverage$rh80,coverage$height80, method = "spearman")
pear_cor_80_test_default <- cor.test(coverage$rh80,coverage$height80, method = "pearson")
spear_cor_80_test_default <- cor.test(coverage$rh80,coverage$height80, method = "spearman")
bias80_default <-round(bias(coverage$rh80,coverage$height80), digits = 4)

RMSE75_default <-round(hydroGOF::rmse(coverage$rh75,coverage$height75), digits = 4)
r2_75_default <- round(rsq(coverage$rh75,coverage$height75), digits = 4)
pear_cor_75_default <- cor(coverage$rh75,coverage$height75, method = "pearson")
spear_cor_75_default <- cor(coverage$rh75,coverage$height75, method = "spearman")
pear_cor_75_test_default <- cor.test(coverage$rh75,coverage$height75, method = "pearson")
spear_cor_75_test_default <- cor.test(coverage$rh75,coverage$height75, method = "spearman")
bias75_default <-round(bias(coverage$rh75,coverage$height75), digits = 4)

RMSE70_default <-round(hydroGOF::rmse(coverage$rh70,coverage$height70), digits = 4)
r2_70_default <- round(rsq(coverage$rh70,coverage$height70), digits = 4)
pear_cor_70_default <- cor(coverage$rh70,coverage$height70, method = "pearson")
spear_cor_70_default <- cor(coverage$rh70,coverage$height70, method = "spearman")
pear_cor_70_test_default <- cor.test(coverage$rh70,coverage$height70, method = "pearson")
spear_cor_70_test_default <- cor.test(coverage$rh70,coverage$height70, method = "spearman")
bias70_default <-round(bias(coverage$rh70,coverage$height70), digits = 4)

RMSE65_default <-round(hydroGOF::rmse(coverage$rh65,coverage$height65), digits = 4)
r2_65_default <- round(rsq(coverage$rh65,coverage$height65), digits = 4)
pear_cor_65_default <- cor(coverage$rh65,coverage$height65, method = "pearson")
spear_cor_65_default <- cor(coverage$rh65,coverage$height65, method = "spearman")
pear_cor_65_test_default <- cor.test(coverage$rh65,coverage$height65, method = "pearson")
spear_cor_65_test_default <- cor.test(coverage$rh65,coverage$height65, method = "spearman")
bias65_default <-round(bias(coverage$rh65,coverage$height65), digits = 4)

# 90 is best with r2 of 0.6606
```

```{r,}
par(mfrow=c(2,1))
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("100th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE100), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_100), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias100), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p2 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("99th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE99), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_99), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias99), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("98th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE98), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_98), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias98), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("95th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE95), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_95), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias95), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("90th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE90), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_90), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias90), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("85th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE85), col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_85), col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias85), col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p7 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height80,rh80), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("80th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE80), alpha = .5,col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_80), alpha = .5,col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias80), alpha = .5,col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p8 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height75,rh75), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("75th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE75), alpha = .5,col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_75), alpha = .5,col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias75), alpha = .5,col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
p9 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height70,rh70), alpha = .5,col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  xlim(0, 55)+ylim(0, 55)+
  ylab("GEDI")+xlab("Drone Lidar")+ggtitle("70th Percentile")+
  geom_text(aes(x = 7, y = 50, label = RMSE70), alpha = .5,col = "red")+
  geom_text(aes(x = 7, y = 40, label = r2_70), alpha = .5,col = "darkgreen")+
  geom_text(aes(x = 7, y = 30, label = bias70), alpha = .5,col = "purple")+ theme(plot.title = element_text(size=10, 
                                                                                                            family="serif"), 
                                                                                  axis.title.x=element_text(size=10, 
                                                                                                           family="serif"),
                                                                                  axis.title.y=element_text(size=10, 
                                                                                                           family="serif"))
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=3)
```




#----------------------------------------------#
#----------------------------------------------#
##---------------- Algorithm 2------------------
#----------------------------------------------#
#----------------------------------------------#
```{r}
# Calculate R squared and RMSE 
RMSE100_a2 <- round(hydroGOF::rmse(coverage$rh100_a2,coverage$height100), digits = 4)
r2_100_a2 <- round(rsq(coverage$rh100_a2,coverage$height100), digits = 4)
pear_cor_100_a2 <- cor(coverage$rh100_a2,coverage$height100, method = "pearson")
spear_cor_100_a2 <- cor(coverage$rh100_a2,coverage$height100, method = "spearman")
pear_cor_100_test_a2 <- cor.test(coverage$rh100_a2,coverage$height100, method = "pearson")
spear_cor_100_test_a2 <- cor.test(coverage$rh100_a2,coverage$height100, method = "spearman")
bias100_a2 <- round(bias(coverage$rh100_a2,coverage$height100), digits = 4)

RMSE99_a2 <-round(hydroGOF::rmse(coverage$rh99_a2,coverage$height99), digits = 4)
r2_99_a2 <- round(rsq(coverage$rh99_a2,coverage$height99), digits = 4)
pear_cor_99_a2 <- cor(coverage$rh99_a2,coverage$height99, method = "pearson")
spear_cor_99_a2 <- cor(coverage$rh99_a2,coverage$height99, method = "spearman")
pear_cor_99_test_a2 <- cor.test(coverage$rh99_a2,coverage$height99, method = "pearson")
spear_cor_99_test_a2 <- cor.test(coverage$rh99_a2,coverage$height99, method = "spearman")
bias99_a2 <-round(bias(coverage$rh99_a2,coverage$height99), digits = 4)

RMSE98_a2 <-round(hydroGOF::rmse(coverage$rh98_a2,coverage$height98), digits = 4)
r2_98_a2 <- round(rsq(coverage$rh98_a2,coverage$height98), digits = 4)
pear_cor_98_a2 <- cor(coverage$rh98_a2,coverage$height98, method = "pearson")
spear_cor_98_a2 <- cor(coverage$rh98_a2,coverage$height98, method = "spearman")
pear_cor_98_test_a2 <- cor.test(coverage$rh98_a2,coverage$height98, method = "pearson")
spear_cor_98_test_a2 <- cor.test(coverage$rh98_a2,coverage$height98, method = "spearman")
bias98_a2 <-round(bias(coverage$rh98_a2,coverage$height98), digits = 4)

RMSE95_a2 <-round(hydroGOF::rmse(coverage$rh95_a2,coverage$height95), digits = 4)
r2_95_a2 <- round(rsq(coverage$rh95_a2,coverage$height95), digits = 4)
pear_cor_95_a2 <- cor(coverage$rh95_a2,coverage$height95, method = "pearson")
spear_cor_95_a2 <- cor(coverage$rh95_a2,coverage$height95, method = "spearman")
pear_cor_95_test_a2 <- cor.test(coverage$rh95_a2,coverage$height95, method = "pearson")
spear_cor_95_test_a2 <- cor.test(coverage$rh95_a2,coverage$height95, method = "spearman")
bias95_a2 <-round(bias(coverage$rh95_a2,coverage$height95), digits = 4)

RMSE90_a2 <-round(hydroGOF::rmse(coverage$rh90_a2,coverage$height90), digits = 4)
r2_90_a2 <- round(rsq(coverage$rh90_a2,coverage$height90), digits = 4)
pear_cor_90_a2 <- cor(coverage$rh90_a2,coverage$height90, method = "pearson")
spear_cor_90_a2 <- cor(coverage$rh90_a2,coverage$height90, method = "spearman")
pear_cor_90_test_a2 <- cor.test(coverage$rh90_a2,coverage$height90, method = "pearson")
spear_cor_90_test_a2 <- cor.test(coverage$rh90_a2,coverage$height90, method = "spearman")
bias90_a2 <-round(bias(coverage$rh90_a2,coverage$height90), digits = 4)

RMSE85_a2 <-round(hydroGOF::rmse(coverage$rh85_a2,coverage$height85), digits = 4)
r2_85_a2 <- round(rsq(coverage$rh85_a2,coverage$height85), digits = 4)
pear_cor_85_a2 <- cor(coverage$rh85_a2,coverage$height85, method = "pearson")
spear_cor_85_a2 <- cor(coverage$rh85_a2,coverage$height85, method = "spearman")
pear_cor_85_test_a2 <- cor.test(coverage$rh85_a2,coverage$height85, method = "pearson")
spear_cor_85_test_a2 <- cor.test(coverage$rh85_a2,coverage$height85, method = "spearman")
bias85_a2 <-round(bias(coverage$rh85_a2,coverage$height85), digits = 4)

RMSE80_a2 <-round(hydroGOF::rmse(coverage$rh80_a2,coverage$height80), digits = 4)
r2_80_a2 <- round(rsq(coverage$rh80_a2,coverage$height80), digits = 4)
pear_cor_80_a2 <- cor(coverage$rh80_a2,coverage$height80, method = "pearson")
spear_cor_80_a2 <- cor(coverage$rh80_a2,coverage$height80, method = "spearman")
pear_cor_80_test_a2 <- cor.test(coverage$rh80_a2,coverage$height80, method = "pearson")
spear_cor_80_test_a2 <- cor.test(coverage$rh80_a2,coverage$height80, method = "spearman")
bias80_a2 <-round(bias(coverage$rh80_a2,coverage$height80), digits = 4)

RMSE75_a2 <-round(hydroGOF::rmse(coverage$rh75_a2,coverage$height75), digits = 4)
r2_75_a2 <- round(rsq(coverage$rh75_a2,coverage$height75), digits = 4)
pear_cor_75_a2 <- cor(coverage$rh75_a2,coverage$height75, method = "pearson")
spear_cor_75_a2 <- cor(coverage$rh75_a2,coverage$height75, method = "spearman")
pear_cor_75_test_a2 <- cor.test(coverage$rh75_a2,coverage$height75, method = "pearson")
spear_cor_75_test_a2 <- cor.test(coverage$rh75_a2,coverage$height75, method = "spearman")
bias75_a2 <-round(bias(coverage$rh75_a2,coverage$height75), digits = 4)

RMSE70_a2 <-round(hydroGOF::rmse(coverage$rh70_a2,coverage$height70), digits = 4)
r2_70_a2 <- round(rsq(coverage$rh70_a2,coverage$height70), digits = 4)
pear_cor_70_a2 <- cor(coverage$rh70_a2,coverage$height70, method = "pearson")
spear_cor_70_a2 <- cor(coverage$rh70_a2,coverage$height70, method = "spearman")
pear_cor_70_test_a2 <- cor.test(coverage$rh70_a2,coverage$height70, method = "pearson")
spear_cor_70_test_a2 <- cor.test(coverage$rh70_a2,coverage$height70, method = "spearman")
bias70_a2 <-round(bias(coverage$rh70_a2,coverage$height70), digits = 4)

RMSE65_a2 <-round(hydroGOF::rmse(coverage$rh65_a2,coverage$height65), digits = 4)
r2_65_a2 <- round(rsq(coverage$rh65_a2,coverage$height65), digits = 4)
pear_cor_65_a2<- cor(coverage$rh65_a2,coverage$height65, method = "pearson")
spear_cor_65_a2 <- cor(coverage$rh65_a2,coverage$height65, method = "spearman")
pear_cor_65_test_a2 <- cor.test(coverage$rh65_a2,coverage$height65, method = "pearson")
spear_cor_65_test_a2 <- cor.test(coverage$rh65_a2,coverage$height65, method = "spearman")
bias65_a2 <-round(bias(coverage$rh65_a2,coverage$height65), digits = 4)

```

```{r,}
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100_a2), col = "purple")
p2 <-coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99_a2), col = "purple")
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98_a2), col = "purple")
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95_a2), col = "purple")
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90_a2), col = "purple")
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85_a2), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85_a2), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85_a2), col = "purple")
```


#----------------------------------------------#
#----------------------------------------------#
##---------------- Algorithm 3------------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE100_a3 <- round(hydroGOF::rmse(coverage$rh100_a3,coverage$height100), digits = 4)
r2_100_a3 <- round(rsq(coverage$rh100_a3,coverage$height100), digits = 4)
pear_cor_100_a3 <- cor(coverage$rh100_a3,coverage$height100, method = "pearson")
spear_cor_100_a3 <- cor(coverage$rh100_a3,coverage$height100, method = "spearman")
pear_cor_100_test_a3 <- cor.test(coverage$rh100_a3,coverage$height100, method = "pearson")
spear_cor_100_test_a3 <- cor.test(coverage$rh100_a3,coverage$height100, method = "spearman")
bias100_a3 <- round(bias(coverage$rh100_a3,coverage$height100), digits = 4)

RMSE99_a3 <-round(hydroGOF::rmse(coverage$rh99_a3,coverage$height99), digits = 4)
r2_99_a3 <- round(rsq(coverage$rh99_a3,coverage$height99), digits = 4)
pear_cor_99_a3 <- cor(coverage$rh99_a3,coverage$height99, method = "pearson")
spear_cor_99_a3 <- cor(coverage$rh99_a3,coverage$height99, method = "spearman")
pear_cor_99_test_a3 <- cor.test(coverage$rh99_a3,coverage$height99, method = "pearson")
spear_cor_99_test_a3 <- cor.test(coverage$rh99_a3,coverage$height99, method = "spearman")
bias99_a3 <-round(bias(coverage$rh99_a3,coverage$height99), digits = 4)

RMSE98_a3 <-round(hydroGOF::rmse(coverage$rh98_a3,coverage$height98), digits = 4)
r2_98_a3 <- round(rsq(coverage$rh98_a3,coverage$height98), digits = 4)
pear_cor_98_a3 <- cor(coverage$rh98_a3,coverage$height98, method = "pearson")
spear_cor_98_a3 <- cor(coverage$rh98_a3,coverage$height98, method = "spearman")
pear_cor_98_test_a3 <- cor.test(coverage$rh98_a3,coverage$height98, method = "pearson")
spear_cor_98_test_a3 <- cor.test(coverage$rh98_a3,coverage$height98, method = "spearman")
bias98_a3 <-round(bias(coverage$rh98_a3,coverage$height98), digits = 4)

RMSE95_a3 <-round(hydroGOF::rmse(coverage$rh95_a3,coverage$height95), digits = 4)
r2_95_a3 <- round(rsq(coverage$rh95_a3,coverage$height95), digits = 4)
pear_cor_95_a3 <- cor(coverage$rh95_a3,coverage$height95, method = "pearson")
spear_cor_95_a3 <- cor(coverage$rh95_a3,coverage$height95, method = "spearman")
pear_cor_95_test_a3 <- cor.test(coverage$rh95_a3,coverage$height95, method = "pearson")
spear_cor_95_test_a3 <- cor.test(coverage$rh95_a3,coverage$height95, method = "spearman")
bias95_a3 <-round(bias(coverage$rh95_a3,coverage$height95), digits = 4)

RMSE90_a3 <-round(hydroGOF::rmse(coverage$rh90_a3,coverage$height90), digits = 4)
r2_90_a3 <- round(rsq(coverage$rh90_a3,coverage$height90), digits = 4)
pear_cor_90_a3 <- cor(coverage$rh90_a3,coverage$height90, method = "pearson")
spear_cor_90_a3 <- cor(coverage$rh90_a3,coverage$height90, method = "spearman")
pear_cor_90_test_a3 <- cor.test(coverage$rh90_a3,coverage$height90, method = "pearson")
spear_cor_90_test_a3 <- cor.test(coverage$rh90_a3,coverage$height90, method = "spearman")
bias90_a3 <-round(bias(coverage$rh90_a3,coverage$height90), digits = 4)

RMSE85_a3 <-round(hydroGOF::rmse(coverage$rh85_a3,coverage$height85), digits = 4)
r2_85_a3 <- round(rsq(coverage$rh85_a3,coverage$height85), digits = 4)
pear_cor_85_a3 <- cor(coverage$rh85_a3,coverage$height85, method = "pearson")
spear_cor_85_a3 <- cor(coverage$rh85_a3,coverage$height85, method = "spearman")
pear_cor_85_test_a3 <- cor.test(coverage$rh85_a3,coverage$height85, method = "pearson")
spear_cor_85_test_a3 <- cor.test(coverage$rh85_a3,coverage$height85, method = "spearman")
bias85_a3 <-round(bias(coverage$rh85_a3,coverage$height85), digits = 4)

RMSE80_a3 <-round(hydroGOF::rmse(coverage$rh80_a3,coverage$height80), digits = 4)
r2_80_a3 <- round(rsq(coverage$rh80_a3,coverage$height80), digits = 4)
pear_cor_80_a3 <- cor(coverage$rh80_a3,coverage$height80, method = "pearson")
spear_cor_80_a3 <- cor(coverage$rh80_a3,coverage$height80, method = "spearman")
pear_cor_80_test_a3 <- cor.test(coverage$rh80_a3,coverage$height80, method = "pearson")
spear_cor_80_test_a3 <- cor.test(coverage$rh80_a3,coverage$height80, method = "spearman")
bias80_a3 <-round(bias(coverage$rh80_a3,coverage$height80), digits = 4)

RMSE75_a3 <-round(hydroGOF::rmse(coverage$rh75_a3,coverage$height75), digits = 4)
r2_75_a3 <- round(rsq(coverage$rh75_a3,coverage$height75), digits = 4)
pear_cor_75_a3 <- cor(coverage$rh75_a3,coverage$height75, method = "pearson")
spear_cor_75_a3 <- cor(coverage$rh75_a3,coverage$height75, method = "spearman")
pear_cor_75_test_a3 <- cor.test(coverage$rh75_a3,coverage$height75, method = "pearson")
spear_cor_75_test_a3 <- cor.test(coverage$rh75_a3,coverage$height75, method = "spearman")
bias75_a3 <-round(bias(coverage$rh75_a3,coverage$height75), digits = 4)

RMSE70_a3 <-round(hydroGOF::rmse(coverage$rh70_a3,coverage$height70), digits = 4)
r2_70_a3 <- round(rsq(coverage$rh70_a3,coverage$height70), digits = 4)
pear_cor_70_a3 <- cor(coverage$rh70_a3,coverage$height70, method = "pearson")
spear_cor_70_a3 <- cor(coverage$rh70_a3,coverage$height70, method = "spearman")
pear_cor_70_test_a3 <- cor.test(coverage$rh70_a3,coverage$height70, method = "pearson")
spear_cor_70_test_a3 <- cor.test(coverage$rh70_a3,coverage$height70, method = "spearman")
bias70_a3 <-round(bias(coverage$rh70_a3,coverage$height70), digits = 4)

RMSE65_a3 <-round(hydroGOF::rmse(coverage$rh65_a3,coverage$height65), digits = 4)
r2_65_a3 <- round(rsq(coverage$rh65_a3,coverage$height65), digits = 4)
pear_cor_65_a3<- cor(coverage$rh65_a3,coverage$height65, method = "pearson")
spear_cor_65_a3 <- cor(coverage$rh65_a3,coverage$height65, method = "spearman")
pear_cor_65_test_a3 <- cor.test(coverage$rh65_a3,coverage$height65, method = "pearson")
spear_cor_65_test_a3 <- cor.test(coverage$rh65_a3,coverage$height65, method = "spearman")
bias65_a3 <-round(bias(coverage$rh65_a3,coverage$height65), digits = 4)

```

```{r,}
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100_a3), col = "purple")
p2 <-coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99_a3), col = "purple")
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98_a3), col = "purple")
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95_a3), col = "purple")
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90_a3), col = "purple")
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85_a3), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85_a3), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85_a3), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```


#----------------------------------------------#
#----------------------------------------------#
##---------------- Algorithm 4------------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE100_a4 <- round(hydroGOF::rmse(coverage$rh100_a4,coverage$height100), digits = 4)
r2_100_a4 <- round(rsq(coverage$rh100_a4,coverage$height100), digits = 4)
pear_cor_100_a4 <- cor(coverage$rh100_a4,coverage$height100, method = "pearson")
spear_cor_100_a4 <- cor(coverage$rh100_a4,coverage$height100, method = "spearman")
pear_cor_100_test_a4 <- cor.test(coverage$rh100_a4,coverage$height100, method = "pearson")
spear_cor_100_test_a4 <- cor.test(coverage$rh100_a4,coverage$height100, method = "spearman")
bias100_a4 <- round(bias(coverage$rh100_a4,coverage$height100), digits = 4)

RMSE99_a4 <-round(hydroGOF::rmse(coverage$rh99_a4,coverage$height99), digits = 4)
r2_99_a4 <- round(rsq(coverage$rh99_a4,coverage$height99), digits = 4)
pear_cor_99_a4 <- cor(coverage$rh99_a4,coverage$height99, method = "pearson")
spear_cor_99_a4 <- cor(coverage$rh99_a4,coverage$height99, method = "spearman")
pear_cor_99_test_a4 <- cor.test(coverage$rh99_a4,coverage$height99, method = "pearson")
spear_cor_99_test_a4 <- cor.test(coverage$rh99_a4,coverage$height99, method = "spearman")
bias99_a4 <-round(bias(coverage$rh99_a4,coverage$height99), digits = 4)

RMSE98_a4 <-round(hydroGOF::rmse(coverage$rh98_a4,coverage$height98), digits = 4)
r2_98_a4 <- round(rsq(coverage$rh98_a4,coverage$height98), digits = 4)
pear_cor_98_a4 <- cor(coverage$rh98_a4,coverage$height98, method = "pearson")
spear_cor_98_a4 <- cor(coverage$rh98_a4,coverage$height98, method = "spearman")
pear_cor_98_test_a4 <- cor.test(coverage$rh98_a4,coverage$height98, method = "pearson")
spear_cor_98_test_a4 <- cor.test(coverage$rh98_a4,coverage$height98, method = "spearman")
bias98_a4 <-round(bias(coverage$rh98_a4,coverage$height98), digits = 4)

RMSE95_a4 <-round(hydroGOF::rmse(coverage$rh95_a4,coverage$height95), digits = 4)
r2_95_a4 <- round(rsq(coverage$rh95_a4,coverage$height95), digits = 4)
pear_cor_95_a4 <- cor(coverage$rh95_a4,coverage$height95, method = "pearson")
spear_cor_95_a4 <- cor(coverage$rh95_a4,coverage$height95, method = "spearman")
pear_cor_95_test_a4 <- cor.test(coverage$rh95_a4,coverage$height95, method = "pearson")
spear_cor_95_test_a4 <- cor.test(coverage$rh95_a4,coverage$height95, method = "spearman")
bias95_a4 <-round(bias(coverage$rh95_a4,coverage$height95), digits = 4)

RMSE90_a4 <-round(hydroGOF::rmse(coverage$rh90_a4,coverage$height90), digits = 4)
r2_90_a4 <- round(rsq(coverage$rh90_a4,coverage$height90), digits = 4)
pear_cor_90_a4 <- cor(coverage$rh90_a4,coverage$height90, method = "pearson")
spear_cor_90_a4 <- cor(coverage$rh90_a4,coverage$height90, method = "spearman")
pear_cor_90_test_a4 <- cor.test(coverage$rh90_a4,coverage$height90, method = "pearson")
spear_cor_90_test_a4 <- cor.test(coverage$rh90_a4,coverage$height90, method = "spearman")
bias90_a4 <-round(bias(coverage$rh90_a4,coverage$height90), digits = 4)

RMSE85_a4 <-round(hydroGOF::rmse(coverage$rh85_a4,coverage$height85), digits = 4)
r2_85_a4 <- round(rsq(coverage$rh85_a4,coverage$height85), digits = 4)
pear_cor_85_a4 <- cor(coverage$rh85_a4,coverage$height85, method = "pearson")
spear_cor_85_a4 <- cor(coverage$rh85_a4,coverage$height85, method = "spearman")
pear_cor_85_test_a4 <- cor.test(coverage$rh85_a4,coverage$height85, method = "pearson")
spear_cor_85_test_a4 <- cor.test(coverage$rh85_a4,coverage$height85, method = "spearman")
bias85_a4 <-round(bias(coverage$rh85_a4,coverage$height85), digits = 4)

RMSE80_a4 <-round(hydroGOF::rmse(coverage$rh80_a4,coverage$height80), digits = 4)
r2_80_a4 <- round(rsq(coverage$rh80_a4,coverage$height80), digits = 4)
pear_cor_80_a4 <- cor(coverage$rh80_a4,coverage$height80, method = "pearson")
spear_cor_80_a4 <- cor(coverage$rh80_a4,coverage$height80, method = "spearman")
pear_cor_80_test_a4 <- cor.test(coverage$rh80_a4,coverage$height80, method = "pearson")
spear_cor_80_test_a4 <- cor.test(coverage$rh80_a4,coverage$height80, method = "spearman")
bias80_a4 <-round(bias(coverage$rh80_a4,coverage$height80), digits = 4)

RMSE75_a4 <-round(hydroGOF::rmse(coverage$rh75_a4,coverage$height75), digits = 4)
r2_75_a4 <- round(rsq(coverage$rh75_a4,coverage$height75), digits = 4)
pear_cor_75_a4 <- cor(coverage$rh75_a4,coverage$height75, method = "pearson")
spear_cor_75_a4 <- cor(coverage$rh75_a4,coverage$height75, method = "spearman")
pear_cor_75_test_a4 <- cor.test(coverage$rh75_a4,coverage$height75, method = "pearson")
spear_cor_75_test_a4 <- cor.test(coverage$rh75_a4,coverage$height75, method = "spearman")
bias75_a4 <-round(bias(coverage$rh75_a4,coverage$height75), digits = 4)

RMSE70_a4 <-round(hydroGOF::rmse(coverage$rh70_a4,coverage$height70), digits = 4)
r2_70_a4 <- round(rsq(coverage$rh70_a4,coverage$height70), digits = 4)
pear_cor_70_a4 <- cor(coverage$rh70_a4,coverage$height70, method = "pearson")
spear_cor_70_a4 <- cor(coverage$rh70_a4,coverage$height70, method = "spearman")
pear_cor_70_test_a4 <- cor.test(coverage$rh70_a4,coverage$height70, method = "pearson")
spear_cor_70_test_a4 <- cor.test(coverage$rh70_a4,coverage$height70, method = "spearman")
bias70_a4 <-round(bias(coverage$rh70_a4,coverage$height70), digits = 4)

RMSE65_a4 <-round(hydroGOF::rmse(coverage$rh65_a4,coverage$height65), digits = 4)
r2_65_a4 <- round(rsq(coverage$rh65_a4,coverage$height65), digits = 4)
pear_cor_65_a4<- cor(coverage$rh65_a4,coverage$height65, method = "pearson")
spear_cor_65_a4 <- cor(coverage$rh65_a4,coverage$height65, method = "spearman")
pear_cor_65_test_a4 <- cor.test(coverage$rh65_a4,coverage$height65, method = "pearson")
spear_cor_65_test_a4 <- cor.test(coverage$rh65_a4,coverage$height65, method = "spearman")
bias65_a4 <-round(bias(coverage$rh65_a4,coverage$height65), digits = 4)

```

```{r,}
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100_a4), col = "purple")
p2 <-coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99_a4), col = "purple")
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98_a4), col = "purple")
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95_a4), col = "purple")
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90_a4), col = "purple")
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a4), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85_a4), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85_a4), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85_a4), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```


#----------------------------------------------#
#----------------------------------------------#
##---------------- Algorithm 5------------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE100_a5 <- round(hydroGOF::rmse(coverage$rh100_a5,coverage$height100), digits = 4)
r2_100_a5 <- round(rsq(coverage$rh100_a5,coverage$height100), digits = 4)
pear_cor_100_a5 <- cor(coverage$rh100_a5,coverage$height100, method = "pearson")
spear_cor_100_a5 <- cor(coverage$rh100_a5,coverage$height100, method = "spearman")
pear_cor_100_test_a5 <- cor.test(coverage$rh100_a5,coverage$height100, method = "pearson")
spear_cor_100_test_a5 <- cor.test(coverage$rh100_a5,coverage$height100, method = "spearman")
bias100_a5 <- round(bias(coverage$rh100_a5,coverage$height100), digits = 4)

RMSE99_a5 <-round(hydroGOF::rmse(coverage$rh99_a5,coverage$height99), digits = 4)
r2_99_a5 <- round(rsq(coverage$rh99_a5,coverage$height99), digits = 4)
pear_cor_99_a5 <- cor(coverage$rh99_a5,coverage$height99, method = "pearson")
spear_cor_99_a5 <- cor(coverage$rh99_a5,coverage$height99, method = "spearman")
pear_cor_99_test_a5 <- cor.test(coverage$rh99_a5,coverage$height99, method = "pearson")
spear_cor_99_test_a5 <- cor.test(coverage$rh99_a5,coverage$height99, method = "spearman")
bias99_a5 <-round(bias(coverage$rh99_a5,coverage$height99), digits = 4)

RMSE98_a5 <-round(hydroGOF::rmse(coverage$rh98_a5,coverage$height98), digits = 4)
r2_98_a5 <- round(rsq(coverage$rh98_a5,coverage$height98), digits = 4)
pear_cor_98_a5 <- cor(coverage$rh98_a5,coverage$height98, method = "pearson")
spear_cor_98_a5 <- cor(coverage$rh98_a5,coverage$height98, method = "spearman")
pear_cor_98_test_a5 <- cor.test(coverage$rh98_a5,coverage$height98, method = "pearson")
spear_cor_98_test_a5 <- cor.test(coverage$rh98_a5,coverage$height98, method = "spearman")
bias98_a5 <-round(bias(coverage$rh98_a5,coverage$height98), digits = 4)

RMSE95_a5 <-round(hydroGOF::rmse(coverage$rh95_a5,coverage$height95), digits = 4)
r2_95_a5 <- round(rsq(coverage$rh95_a5,coverage$height95), digits = 4)
pear_cor_95_a5 <- cor(coverage$rh95_a5,coverage$height95, method = "pearson")
spear_cor_95_a5 <- cor(coverage$rh95_a5,coverage$height95, method = "spearman")
pear_cor_95_test_a5 <- cor.test(coverage$rh95_a5,coverage$height95, method = "pearson")
spear_cor_95_test_a5 <- cor.test(coverage$rh95_a5,coverage$height95, method = "spearman")
bias95_a5 <-round(bias(coverage$rh95_a5,coverage$height95), digits = 4)

RMSE90_a5 <-round(hydroGOF::rmse(coverage$rh90_a5,coverage$height90), digits = 4)
r2_90_a5 <- round(rsq(coverage$rh90_a5,coverage$height90), digits = 4)
pear_cor_90_a5 <- cor(coverage$rh90_a5,coverage$height90, method = "pearson")
spear_cor_90_a5 <- cor(coverage$rh90_a5,coverage$height90, method = "spearman")
pear_cor_90_test_a5 <- cor.test(coverage$rh90_a5,coverage$height90, method = "pearson")
spear_cor_90_test_a5 <- cor.test(coverage$rh90_a5,coverage$height90, method = "spearman")
bias90_a5 <-round(bias(coverage$rh90_a5,coverage$height90), digits = 4)

RMSE85_a5 <-round(hydroGOF::rmse(coverage$rh85_a5,coverage$height85), digits = 4)
r2_85_a5 <- round(rsq(coverage$rh85_a5,coverage$height85), digits = 4)
pear_cor_85_a5 <- cor(coverage$rh85_a5,coverage$height85, method = "pearson")
spear_cor_85_a5 <- cor(coverage$rh85_a5,coverage$height85, method = "spearman")
pear_cor_85_test_a5 <- cor.test(coverage$rh85_a5,coverage$height85, method = "pearson")
spear_cor_85_test_a5 <- cor.test(coverage$rh85_a5,coverage$height85, method = "spearman")
bias85_a5 <-round(bias(coverage$rh85_a5,coverage$height85), digits = 4)

RMSE80_a5 <-round(hydroGOF::rmse(coverage$rh80_a5,coverage$height80), digits = 4)
r2_80_a5 <- round(rsq(coverage$rh80_a5,coverage$height80), digits = 4)
pear_cor_80_a5 <- cor(coverage$rh80_a5,coverage$height80, method = "pearson")
spear_cor_80_a5 <- cor(coverage$rh80_a5,coverage$height80, method = "spearman")
pear_cor_80_test_a5 <- cor.test(coverage$rh80_a5,coverage$height80, method = "pearson")
spear_cor_80_test_a5 <- cor.test(coverage$rh80_a5,coverage$height80, method = "spearman")
bias80_a5 <-round(bias(coverage$rh80_a5,coverage$height80), digits = 4)

RMSE75_a5 <-round(hydroGOF::rmse(coverage$rh75_a5,coverage$height75), digits = 4)
r2_75_a5 <- round(rsq(coverage$rh75_a5,coverage$height75), digits = 4)
pear_cor_75_a5 <- cor(coverage$rh75_a5,coverage$height75, method = "pearson")
spear_cor_75_a5 <- cor(coverage$rh75_a5,coverage$height75, method = "spearman")
pear_cor_75_test_a5 <- cor.test(coverage$rh75_a5,coverage$height75, method = "pearson")
spear_cor_75_test_a5 <- cor.test(coverage$rh75_a5,coverage$height75, method = "spearman")
bias75_a5 <-round(bias(coverage$rh75_a5,coverage$height75), digits = 4)

RMSE70_a5 <-round(hydroGOF::rmse(coverage$rh70_a5,coverage$height70), digits = 4)
r2_70_a5 <- round(rsq(coverage$rh70_a5,coverage$height70), digits = 4)
pear_cor_70_a5 <- cor(coverage$rh70_a5,coverage$height70, method = "pearson")
spear_cor_70_a5 <- cor(coverage$rh70_a5,coverage$height70, method = "spearman")
pear_cor_70_test_a5 <- cor.test(coverage$rh70_a5,coverage$height70, method = "pearson")
spear_cor_70_test_a5 <- cor.test(coverage$rh70_a5,coverage$height70, method = "spearman")
bias70_a5 <-round(bias(coverage$rh70_a5,coverage$height70), digits = 4)

RMSE65_a5 <-round(hydroGOF::rmse(coverage$rh65_a5,coverage$height65), digits = 4)
r2_65_a5 <- round(rsq(coverage$rh65_a5,coverage$height65), digits = 4)
pear_cor_65_a5<- cor(coverage$rh65_a5,coverage$height65, method = "pearson")
spear_cor_65_a5 <- cor(coverage$rh65_a5,coverage$height65, method = "spearman")
pear_cor_65_test_a5 <- cor.test(coverage$rh65_a5,coverage$height65, method = "pearson")
spear_cor_65_test_a5 <- cor.test(coverage$rh65_a5,coverage$height65, method = "spearman")
bias65_a5 <-round(bias(coverage$rh65_a5,coverage$height65), digits = 4)

```

```{r,}
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100_a5), col = "purple")
p2 <-coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99_a5), col = "purple")
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98_a5), col = "purple")
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95_a5), col = "purple")
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90_a5), col = "purple")
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a5), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85_a5), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85_a5), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85_a5), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

#----------------------------------------------#
#----------------------------------------------#
##---------------- Algorithm 6------------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE100_a6 <- round(hydroGOF::rmse(coverage$rh100_a6,coverage$height100), digits = 4)
r2_100_a6 <- round(rsq(coverage$rh100_a6,coverage$height100), digits = 4)
pear_cor_100_a6 <- cor(coverage$rh100_a6,coverage$height100, method = "pearson")
spear_cor_100_a6 <- cor(coverage$rh100_a6,coverage$height100, method = "spearman")
pear_cor_100_test_a6 <- cor.test(coverage$rh100_a6,coverage$height100, method = "pearson")
spear_cor_100_test_a6 <- cor.test(coverage$rh100_a6,coverage$height100, method = "spearman")
bias100_a6 <- round(bias(coverage$rh100_a6,coverage$height100), digits = 4)

RMSE99_a6 <-round(hydroGOF::rmse(coverage$rh99_a6,coverage$height99), digits = 4)
r2_99_a6 <- round(rsq(coverage$rh99_a6,coverage$height99), digits = 4)
pear_cor_99_a6 <- cor(coverage$rh99_a6,coverage$height99, method = "pearson")
spear_cor_99_a6 <- cor(coverage$rh99_a6,coverage$height99, method = "spearman")
pear_cor_99_test_a6 <- cor.test(coverage$rh99_a6,coverage$height99, method = "pearson")
spear_cor_99_test_a6 <- cor.test(coverage$rh99_a6,coverage$height99, method = "spearman")
bias99_a6 <-round(bias(coverage$rh99_a6,coverage$height99), digits = 4)

RMSE98_a6 <-round(hydroGOF::rmse(coverage$rh98_a6,coverage$height98), digits = 4)
r2_98_a6 <- round(rsq(coverage$rh98_a6,coverage$height98), digits = 4)
pear_cor_98_a6 <- cor(coverage$rh98_a6,coverage$height98, method = "pearson")
spear_cor_98_a6 <- cor(coverage$rh98_a6,coverage$height98, method = "spearman")
pear_cor_98_test_a6 <- cor.test(coverage$rh98_a6,coverage$height98, method = "pearson")
spear_cor_98_test_a6 <- cor.test(coverage$rh98_a6,coverage$height98, method = "spearman")
bias98_a6 <-round(bias(coverage$rh98_a6,coverage$height98), digits = 4)

RMSE95_a6 <-round(hydroGOF::rmse(coverage$rh95_a6,coverage$height95), digits = 4)
r2_95_a6 <- round(rsq(coverage$rh95_a6,coverage$height95), digits = 4)
pear_cor_95_a6 <- cor(coverage$rh95_a6,coverage$height95, method = "pearson")
spear_cor_95_a6 <- cor(coverage$rh95_a6,coverage$height95, method = "spearman")
pear_cor_95_test_a6 <- cor.test(coverage$rh95_a6,coverage$height95, method = "pearson")
spear_cor_95_test_a6 <- cor.test(coverage$rh95_a6,coverage$height95, method = "spearman")
bias95_a6 <-round(bias(coverage$rh95_a6,coverage$height95), digits = 4)

RMSE90_a6 <-round(hydroGOF::rmse(coverage$rh90_a6,coverage$height90), digits = 4)
r2_90_a6 <- round(rsq(coverage$rh90_a6,coverage$height90), digits = 4)
pear_cor_90_a6 <- cor(coverage$rh90_a6,coverage$height90, method = "pearson")
spear_cor_90_a6 <- cor(coverage$rh90_a6,coverage$height90, method = "spearman")
pear_cor_90_test_a6 <- cor.test(coverage$rh90_a6,coverage$height90, method = "pearson")
spear_cor_90_test_a6 <- cor.test(coverage$rh90_a6,coverage$height90, method = "spearman")
bias90_a6 <-round(bias(coverage$rh90_a6,coverage$height90), digits = 4)

RMSE85_a6 <-round(hydroGOF::rmse(coverage$rh85_a6,coverage$height85), digits = 4)
r2_85_a6 <- round(rsq(coverage$rh85_a6,coverage$height85), digits = 4)
pear_cor_85_a6 <- cor(coverage$rh85_a6,coverage$height85, method = "pearson")
spear_cor_85_a6 <- cor(coverage$rh85_a6,coverage$height85, method = "spearman")
pear_cor_85_test_a6 <- cor.test(coverage$rh85_a6,coverage$height85, method = "pearson")
spear_cor_85_test_a6 <- cor.test(coverage$rh85_a6,coverage$height85, method = "spearman")
bias85_a6 <-round(bias(coverage$rh85_a6,coverage$height85), digits = 4)

RMSE80_a6 <-round(hydroGOF::rmse(coverage$rh80_a6,coverage$height80), digits = 4)
r2_80_a6 <- round(rsq(coverage$rh80_a6,coverage$height80), digits = 4)
pear_cor_80_a6 <- cor(coverage$rh80_a6,coverage$height80, method = "pearson")
spear_cor_80_a6 <- cor(coverage$rh80_a6,coverage$height80, method = "spearman")
pear_cor_80_test_a6 <- cor.test(coverage$rh80_a6,coverage$height80, method = "pearson")
spear_cor_80_test_a6 <- cor.test(coverage$rh80_a6,coverage$height80, method = "spearman")
bias80_a6 <-round(bias(coverage$rh80_a6,coverage$height80), digits = 4)

RMSE75_a6 <-round(hydroGOF::rmse(coverage$rh75_a6,coverage$height75), digits = 4)
r2_75_a6 <- round(rsq(coverage$rh75_a6,coverage$height75), digits = 4)
pear_cor_75_a6 <- cor(coverage$rh75_a6,coverage$height75, method = "pearson")
spear_cor_75_a6 <- cor(coverage$rh75_a6,coverage$height75, method = "spearman")
pear_cor_75_test_a6 <- cor.test(coverage$rh75_a6,coverage$height75, method = "pearson")
spear_cor_75_test_a6 <- cor.test(coverage$rh75_a6,coverage$height75, method = "spearman")
bias75_a6 <-round(bias(coverage$rh75_a6,coverage$height75), digits = 4)

RMSE70_a6 <-round(hydroGOF::rmse(coverage$rh70_a6,coverage$height70), digits = 4)
r2_70_a6 <- round(rsq(coverage$rh70_a6,coverage$height70), digits = 4)
pear_cor_70_a6 <- cor(coverage$rh70_a6,coverage$height70, method = "pearson")
spear_cor_70_a6 <- cor(coverage$rh70_a6,coverage$height70, method = "spearman")
pear_cor_70_test_a6 <- cor.test(coverage$rh70_a6,coverage$height70, method = "pearson")
spear_cor_70_test_a6 <- cor.test(coverage$rh70_a6,coverage$height70, method = "spearman")
bias70_a6 <-round(bias(coverage$rh70_a6,coverage$height70), digits = 4)

RMSE65_a6 <-round(hydroGOF::rmse(coverage$rh65_a6,coverage$height65), digits = 4)
r2_65_a6 <- round(rsq(coverage$rh65_a6,coverage$height65), digits = 4)
pear_cor_65_a6<- cor(coverage$rh65_a6,coverage$height65, method = "pearson")
spear_cor_65_a6 <- cor(coverage$rh65_a6,coverage$height65, method = "spearman")
pear_cor_65_test_a6 <- cor.test(coverage$rh65_a6,coverage$height65, method = "pearson")
spear_cor_65_test_a6 <- cor.test(coverage$rh65_a6,coverage$height65, method = "spearman")
bias65_a6 <-round(bias(coverage$rh65_a6,coverage$height65), digits = 4)

```

```{r,}
p1 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100_a6), col = "purple")
p2 <-coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99_a6), col = "purple")
p3 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98_a6), col = "purple")
p4 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95_a6), col = "purple")
p5 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90_a6), col = "purple")
p6 <- coverage %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a6), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85_a6), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85_a6), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85_a6), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

#----------------------------------------------#
#----------------------------------------------#
##--------------Results Dataframe--------------
#----------------------------------------------#
#----------------------------------------------#
```{r,}
# make a dataframe with all stats results
algs <- c("_default","_a2","_a3","_a4","_a5","_a6")
percentiles <- c(100, 99, 98, 95, 90, 85, 80, 75, 70, 65)
stats <- c("RMSE", "r2_", "pear_cor_", "spear_cor_", "bias")

for (i in 1:length(algs)){
  #percentiles down, stats across
  df <- data.frame(matrix(ncol = length(stats), nrow = length(percentiles)))
  colnames(df) <- stats
  for (j in 1:length(percentiles)){
    temp <- paste0(percentiles[j], algs[i])
    for (k in 1:length(stats)){
      var <- lapply(paste0(stats[k], temp),get)
      df[j,k] <- var
      
    }
  }
df$percentile <- percentiles
df$algorithm <- rep(algs[i],length(nrow(df)))
algname <-paste0(algs[i], i)
assign(paste0("stats", algname), df)
}
```




#----------------------------------------------#
#----------------------------------------------#
##-----------Elevation Comparisons--------------
#----------------------------------------------#
#----------------------------------------------#

```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_default, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_default, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_default, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_default, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_default), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```

## Algorithm 2

```{r}
# Calculate R squared and RMSE 
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_a2,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_a2,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_a2,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_a2,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_a2,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_a2,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_a2,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_a2,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_a2,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_a2,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_a2,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_a2,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_a2,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_a2,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_a2,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_a2,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_a2,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_a2,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_a2,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_a2,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_a2,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_a2,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_a2,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_a2,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_a2,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_a2,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_a2,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_a2,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_a2,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_a2,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_a2,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_a2,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_a2,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_a2,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_a2,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_a2,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_a2,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_a2,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_a2,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_a2,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_a2,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_a2,plotdat$height85), digits = 4)

RMSE80 <-round(hydroGOF::rmse(plotdat$rh80_a2,plotdat$height80), digits = 4)
r2_80 <- round(rsq(plotdat$rh80_a2,plotdat$height80), digits = 4)
pear_cor_80 <- cor(plotdat$rh80_a2,plotdat$height80, method = "pearson")
spear_cor_80 <- cor(plotdat$rh80_a2,plotdat$height80, method = "spearman")
pear_cor_80_test <- cor.test(plotdat$rh80_a2,plotdat$height80, method = "pearson")
spear_cor_80_test <- cor.test(plotdat$rh80_a2,plotdat$height80, method = "spearman")
bias80 <-round(bias(plotdat$rh80_a2,plotdat$height80), digits = 4)

RMSE75 <-round(hydroGOF::rmse(plotdat$rh75_a2,plotdat$height75), digits = 4)
r2_75 <- round(rsq(plotdat$rh75_a2,plotdat$height75), digits = 4)
pear_cor_75 <- cor(plotdat$rh75_a2,plotdat$height75, method = "pearson")
spear_cor_75 <- cor(plotdat$rh75_a2,plotdat$height75, method = "spearman")
pear_cor_75_test <- cor.test(plotdat$rh75_a2,plotdat$height75, method = "pearson")
spear_cor_75_test <- cor.test(plotdat$rh75_a2,plotdat$height75, method = "spearman")
bias75 <-round(bias(plotdat$rh75_a2,plotdat$height75), digits = 4)

RMSE70 <-round(hydroGOF::rmse(plotdat$rh70_a2,plotdat$height70), digits = 4)
r2_70 <- round(rsq(plotdat$rh70_a2,plotdat$height70), digits = 4)
pear_cor_70 <- cor(plotdat$rh70_a2,plotdat$height70, method = "pearson")
spear_cor_70 <- cor(plotdat$rh70_a2,plotdat$height70, method = "spearman")
pear_cor_70_test <- cor.test(plotdat$rh70_a2,plotdat$height70, method = "pearson")
spear_cor_70_test <- cor.test(plotdat$rh70_a2,plotdat$height70, method = "spearman")
bias70 <-round(bias(plotdat$rh70_a2,plotdat$height70), digits = 4)

RMSE65 <-round(hydroGOF::rmse(plotdat$rh65_a2,plotdat$height65), digits = 4)
r2_65 <- round(rsq(plotdat$rh65_a2,plotdat$height65), digits = 4)
pear_cor_65 <- cor(plotdat$rh65_a2,plotdat$height65, method = "pearson")
spear_cor_65 <- cor(plotdat$rh65_a2,plotdat$height65, method = "spearman")
pear_cor_65_test <- cor.test(plotdat$rh65_a2,plotdat$height65, method = "pearson")
spear_cor_65_test <- cor.test(plotdat$rh65_a2,plotdat$height65, method = "spearman")
bias65 <-round(bias(plotdat$rh65_a2,plotdat$height65), digits = 4)

```

```{r,}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```


```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a2, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a2, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a2, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a2, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_a2), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_a2), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
## Algorithm 3

```{r}
# Calculate R squared and RMSE 
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_a3,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_a3,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_a3,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_a3,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_a3,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_a3,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_a3,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_a3,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_a3,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_a3,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_a3,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_a3,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_a3,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_a3,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_a3,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_a3,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_a3,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_a3,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_a3,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_a3,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_a3,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_a3,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_a3,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_a3,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_a3,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_a3,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_a3,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_a3,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_a3,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_a3,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_a3,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_a3,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_a3,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_a3,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_a3,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_a3,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_a3,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_a3,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_a3,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_a3,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_a3,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_a3,plotdat$height85), digits = 4)

RMSE80 <-round(hydroGOF::rmse(plotdat$rh80_a3,plotdat$height80), digits = 4)
r2_80 <- round(rsq(plotdat$rh80_a3,plotdat$height80), digits = 4)
pear_cor_80 <- cor(plotdat$rh80_a3,plotdat$height80, method = "pearson")
spear_cor_80 <- cor(plotdat$rh80_a3,plotdat$height80, method = "spearman")
pear_cor_80_test <- cor.test(plotdat$rh80_a3,plotdat$height80, method = "pearson")
spear_cor_80_test <- cor.test(plotdat$rh80_a3,plotdat$height80, method = "spearman")
bias80 <-round(bias(plotdat$rh80_a3,plotdat$height80), digits = 4)

RMSE80
RMSE75
r2_85
r2_80
r2_75
r2_70
r2_65
bias80
bias75

RMSE75 <-round(hydroGOF::rmse(plotdat$rh75_a3,plotdat$height75), digits = 4)
r2_75 <- round(rsq(plotdat$rh75_a3,plotdat$height75), digits = 4)
pear_cor_75 <- cor(plotdat$rh75_a3,plotdat$height75, method = "pearson")
spear_cor_75 <- cor(plotdat$rh75_a3,plotdat$height75, method = "spearman")
pear_cor_75_test <- cor.test(plotdat$rh75_a3,plotdat$height75, method = "pearson")
spear_cor_75_test <- cor.test(plotdat$rh75_a3,plotdat$height75, method = "spearman")
bias75 <-round(bias(plotdat$rh75_a3,plotdat$height75), digits = 4)

RMSE70 <-round(hydroGOF::rmse(plotdat$rh70_a3,plotdat$height70), digits = 4)
r2_70 <- round(rsq(plotdat$rh70_a3,plotdat$height70), digits = 4)
pear_cor_70 <- cor(plotdat$rh70_a3,plotdat$height70, method = "pearson")
spear_cor_70 <- cor(plotdat$rh70_a3,plotdat$height70, method = "spearman")
pear_cor_70_test <- cor.test(plotdat$rh70_a3,plotdat$height70, method = "pearson")
spear_cor_70_test <- cor.test(plotdat$rh70_a3,plotdat$height70, method = "spearman")
bias70 <-round(bias(plotdat$rh70_a3,plotdat$height70), digits = 4)

RMSE65 <-round(hydroGOF::rmse(plotdat$rh65_a3,plotdat$height65), digits = 4)
r2_65 <- round(rsq(plotdat$rh65_a3,plotdat$height65), digits = 4)
pear_cor_65 <- cor(plotdat$rh65_a3,plotdat$height65, method = "pearson")
spear_cor_65 <- cor(plotdat$rh65_a3,plotdat$height65, method = "spearman")
pear_cor_65_test <- cor.test(plotdat$rh65_a3,plotdat$height65, method = "pearson")
spear_cor_65_test <- cor.test(plotdat$rh65_a3,plotdat$height65, method = "spearman")
bias65 <-round(bias(plotdat$rh65_a3,plotdat$height65), digits = 4)
```

```{r,}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a3, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$Elevation_a3, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a3, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$Elevation_a3, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$Elevation_a3), digits = 4)
```

```{r,}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,Elevation_a3), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```
Comparison of Copernicus and drone lidar elevation
```{r}
# Calculate R squared and RMSE 
RMSE_elev <- round(hydroGOF::rmse(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
r2_elev <- round(rsq(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
pear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$coper_elev, method = "pearson")
spear_cor_95_elev <- cor(plotdat$lidar_elev,plotdat$coper_elev, method = "spearman")
pear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$coper_elev, method = "pearson")
spear_cor_95_test_elev <- cor.test(plotdat$lidar_elev,plotdat$coper_elev, method = "spearman")
bias_elev <- round(bias(plotdat$lidar_elev,plotdat$coper_elev), digits = 4)
```

```{r}
plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(lidar_elev,coper_elev), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 670, y = 730, label = RMSE_elev), col = "red")+
  geom_label(aes(x = 670, y = 720, label = r2_elev), col = "green")+
  geom_label(aes(x = 670, y = 710, label = bias_elev), col = "purple")
```

Height comparisons with copernicus elevation adjustment

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust <- plotdat$Elevation-plotdat$coper_elev
summary(plotdat$elev_adjust)

plotdat$rh100_adj <- plotdat$rh100 + plotdat$elev_adjust
summary(plotdat$rh100_adj)
plotdat$rh99_adj <- plotdat$rh99 + plotdat$elev_adjust
summary(plotdat$rh99_adj)
plotdat$rh98_adj <- plotdat$rh98 + plotdat$elev_adjust
summary(plotdat$rh98_adj)
plotdat$rh95_adj <- plotdat$rh95 + plotdat$elev_adjust
summary(plotdat$rh95_adj)
plotdat$rh90_adj <- plotdat$rh90 + plotdat$elev_adjust
summary(plotdat$rh90_adj)
plotdat$rh85_adj <- plotdat$rh85 + plotdat$elev_adjust
summary(plotdat$rh85_adj)
```
```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

Height comparisons with elevation adjustment

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust <- plotdat$Elevation-plotdat$lidar_elev
summary(plotdat$elev_adjust)

plotdat$rh100_adj <- plotdat$rh100 + plotdat$elev_adjust
summary(plotdat$rh100_adj)
plotdat$rh99_adj <- plotdat$rh99 + plotdat$elev_adjust
summary(plotdat$rh99_adj)
plotdat$rh98_adj <- plotdat$rh98 + plotdat$elev_adjust
summary(plotdat$rh98_adj)
plotdat$rh95_adj <- plotdat$rh95 + plotdat$elev_adjust
summary(plotdat$rh95_adj)
plotdat$rh90_adj <- plotdat$rh90 + plotdat$elev_adjust
summary(plotdat$rh90_adj)
plotdat$rh85_adj <- plotdat$rh85 + plotdat$elev_adjust
summary(plotdat$rh85_adj)
```

```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```

```{r}
# Height adjustment shot by shot
plotdat$elev_adjust_default <- plotdat$Elevation_default-plotdat$lidar_elev
summary(plotdat$elev_adjust_default)

plotdat$rh100_adj_default <- plotdat$rh100 + plotdat$elev_adjust_default
summary(plotdat$rh100_adj_default)
plotdat$rh99_adj_default <- plotdat$rh99 + plotdat$elev_adjust_default
summary(plotdat$rh99_adj_default)
plotdat$rh98_adj_default <- plotdat$rh98 + plotdat$elev_adjust_default
summary(plotdat$rh98_adj_default)
plotdat$rh95_adj_default <- plotdat$rh95 + plotdat$elev_adjust_default
summary(plotdat$rh95_adj_default)
plotdat$rh90_adj_default <- plotdat$rh90 + plotdat$elev_adjust_default
summary(plotdat$rh90_adj_default)
plotdat$rh85_adj_default <- plotdat$rh85 + plotdat$elev_adjust_default
summary(plotdat$rh85_adj_default)
```
```{r}
RMSE100 <- round(hydroGOF::rmse(plotdat$rh100_adj_default,plotdat$height100), digits = 4)
r2_100 <- round(rsq(plotdat$rh100_adj_default,plotdat$height100), digits = 4)
pear_cor_100 <- cor(plotdat$rh100_adj_default,plotdat$height100, method = "pearson")
spear_cor_100 <- cor(plotdat$rh100_adj_default,plotdat$height100, method = "spearman")
pear_cor_100_test <- cor.test(plotdat$rh100_adj_default,plotdat$height100, method = "pearson")
spear_cor_100_test <- cor.test(plotdat$rh100_adj_default,plotdat$height100, method = "spearman")
bias100 <- round(bias(plotdat$rh100_adj_default,plotdat$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(plotdat$rh99_adj_default,plotdat$height99), digits = 4)
r2_99 <- round(rsq(plotdat$rh99_adj_default,plotdat$height99), digits = 4)
pear_cor_99 <- cor(plotdat$rh99_adj_default,plotdat$height99, method = "pearson")
spear_cor_99 <- cor(plotdat$rh99_adj_default,plotdat$height99, method = "spearman")
pear_cor_99_test <- cor.test(plotdat$rh99_adj_default,plotdat$height99, method = "pearson")
spear_cor_99_test <- cor.test(plotdat$rh99_adj_default,plotdat$height99, method = "spearman")
bias99 <-round(bias(plotdat$rh99_adj_default,plotdat$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(plotdat$rh98_adj_default,plotdat$height98), digits = 4)
r2_98 <- round(rsq(plotdat$rh98_adj_default,plotdat$height98), digits = 4)
pear_cor_98 <- cor(plotdat$rh98_adj_default,plotdat$height98, method = "pearson")
spear_cor_98 <- cor(plotdat$rh98_adj_default,plotdat$height98, method = "spearman")
pear_cor_98_test <- cor.test(plotdat$rh98_adj_default,plotdat$height98, method = "pearson")
spear_cor_98_test <- cor.test(plotdat$rh98_adj_default,plotdat$height98, method = "spearman")
bias98 <-round(bias(plotdat$rh98_adj_default,plotdat$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(plotdat$rh95_adj_default,plotdat$height95), digits = 4)
r2_95 <- round(rsq(plotdat$rh95_adj_default,plotdat$height95), digits = 4)
pear_cor_95 <- cor(plotdat$rh95_adj_default,plotdat$height95, method = "pearson")
spear_cor_95 <- cor(plotdat$rh95_adj_default,plotdat$height95, method = "spearman")
pear_cor_95_test <- cor.test(plotdat$rh95_adj_default,plotdat$height95, method = "pearson")
spear_cor_95_test <- cor.test(plotdat$rh95_adj_default,plotdat$height95, method = "spearman")
bias95 <-round(bias(plotdat$rh95_adj_default,plotdat$height95), digits = 4)

RMSE90 <-round(hydroGOF::rmse(plotdat$rh90_adj_default,plotdat$height90), digits = 4)
r2_90 <- round(rsq(plotdat$rh90_adj_default,plotdat$height90), digits = 4)
pear_cor_90 <- cor(plotdat$rh90_adj_default,plotdat$height90, method = "pearson")
spear_cor_90 <- cor(plotdat$rh90_adj_default,plotdat$height90, method = "spearman")
pear_cor_90_test <- cor.test(plotdat$rh90_adj_default,plotdat$height90, method = "pearson")
spear_cor_90_test <- cor.test(plotdat$rh90_adj_default,plotdat$height90, method = "spearman")
bias90 <-round(bias(plotdat$rh90_adj_default,plotdat$height90), digits = 4)

RMSE85 <-round(hydroGOF::rmse(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
r2_85 <- round(rsq(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
pear_cor_85 <- cor(plotdat$rh85_adj_default,plotdat$height85, method = "pearson")
spear_cor_85 <- cor(plotdat$rh85_adj_default,plotdat$height85, method = "spearman")
pear_cor_85_test <- cor.test(plotdat$rh85_adj_default,plotdat$height85, method = "pearson")
spear_cor_85_test <- cor.test(plotdat$rh85_adj_default,plotdat$height85, method = "spearman")
bias85 <-round(bias(plotdat$rh85_adj_default,plotdat$height85), digits = 4)
```

```{r}
p1 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height100,rh100_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE100), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_100), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias100), col = "purple")
p2 <-plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height99,rh99_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE99), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_99), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias99), col = "purple")
p3 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height98,rh98_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE98), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_98), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias98), col = "purple")
p4 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height95,rh95_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE95), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_95), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias95), col = "purple")
p5 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height90,rh90_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE90), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_90), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias90), col = "purple")
p6 <- plotdat %>%
  ggplot() + 
  geom_point(mapping = aes(height85,rh85_adj_default), col = "blue")+
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 15, y = 50, label = RMSE85), col = "red")+
  geom_label(aes(x = 15, y = 40, label = r2_85), col = "green")+
  geom_label(aes(x = 15, y = 30, label = bias85), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, p5, p6, cols=2)
```



### Comparisons between CHM and Ground Data
```{r, echo=FALSE}
grounddat_field_gedi <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_gedi_field_all.csv")
grounddat_field_gedi <- na.omit(grounddat_field_gedi)
grounddat_lidar <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_field_lidar.csv")

str(grounddat_field_gedi$field_height100)
```



```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)
r2_100 <- round(rsq(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)
pear_cor_100 <- cor(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "pearson")
spear_cor_100 <- cor(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_lidar$field_height100 ,grounddat_lidar$height100, method = "spearman")
bias100 <- round(bias(grounddat_lidar$field_height100 ,grounddat_lidar$height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)
r2_99 <- round(rsq(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)
pear_cor_99 <- cor(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "pearson")
spear_cor_99 <- cor(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_lidar$field_height99 ,grounddat_lidar$height99, method = "spearman")
bias99 <-round(bias(grounddat_lidar$field_height99 ,grounddat_lidar$height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)
r2_98 <- round(rsq(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)
pear_cor_98 <- cor(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "pearson")
spear_cor_98 <- cor(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_lidar$field_height98 ,grounddat_lidar$height98, method = "spearman")
bias98 <-round(bias(grounddat_lidar$field_height98 ,grounddat_lidar$height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)
r2_95 <- round(rsq(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)
pear_cor_95 <- cor(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "pearson")
spear_cor_95 <- cor(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_lidar$field_height95 ,grounddat_lidar$height95, method = "spearman")
bias95 <-round(bias(grounddat_lidar$field_height95 ,grounddat_lidar$height95), digits = 4)


r2_90 <- round(rsq(grounddat_lidar$field_height90 ,grounddat_lidar$height90), digits = 4)
r2_85 <- round(rsq(grounddat_lidar$field_height85 ,grounddat_lidar$height85), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height100,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height99,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height98,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(height95,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

### Comparison between Ground and Gedi
## Default
```{r,}
grounddat_field_gedi %>%
  ggplot() + 
  geom_point(mapping = aes(rh100,field_height), col = "blue")+
  geom_abline(intercept = 0, slope = 1)
grounddat_field_gedi %>%
  ggplot() + 
  geom_point(mapping = aes(rh98,field_height), col = "blue")+
  geom_abline(intercept = 0, slope = 1)
```

```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100 ,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99 ,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98 ,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95 ,grounddat_field_gedi$field_height95), digits = 4)

r2_90 <- round(rsq(grounddat_field_gedi$rh90 ,grounddat_field_gedi$field_height90), digits = 4)

r2_85 <- round(rsq(grounddat_field_gedi$rh85 ,grounddat_field_gedi$field_height85), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

## Alg 2
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a2,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a2,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a2,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a2,grounddat_field_gedi$field_height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100_a2,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99_a2,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98_a2,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95_a2,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

## Alg 3
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a3,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a3,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a3,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a3,grounddat_field_gedi$field_height95), digits = 4)
```

```{r,}
p1 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh100_a3,field_height100), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE100), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_100), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias100), col = "purple")
p2 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh99_a3,field_height99), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE99), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_99), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias99), col = "purple")
p3 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh98_a3,field_height98), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE98), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_98), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias98), col = "purple")
p4 <- grounddat_lidar %>%
  ggplot() + 
  geom_point(mapping = aes(rh95_a3,field_height95), col = "blue")+
  xlim(20,70) + ylim(20,70) +
  geom_abline(intercept = 0, slope = 1)+
  geom_label(aes(x = 30, y = 70, label = RMSE95), col = "red")+
  geom_label(aes(x = 30, y = 60, label = r2_95), col = "green")+
  geom_label(aes(x = 30, y = 50, label = bias95), col = "purple")
```

```{r}
multiplot(p1, p2, p3, p4, cols=2)
```

## Alg 4
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100), digits = 4)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100), digits = 4)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a4,grounddat_field_gedi$field_height100), digits = 4)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99), digits = 4)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99), digits = 4)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a4,grounddat_field_gedi$field_height99), digits = 4)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98), digits = 4)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98), digits = 4)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a4,grounddat_field_gedi$field_height98), digits = 4)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95), digits = 4)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95), digits = 4)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a4,grounddat_field_gedi$field_height95), digits = 4)
```



## Alg 5
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100), digits = 5)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100), digits = 5)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a5,grounddat_field_gedi$field_height100), digits = 5)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99), digits = 5)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99), digits = 5)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a5,grounddat_field_gedi$field_height99), digits = 5)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98), digits = 5)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98), digits = 5)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a5,grounddat_field_gedi$field_height98), digits = 5)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95), digits = 5)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95), digits = 5)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a5,grounddat_field_gedi$field_height95), digits = 5)
```

## Alg 6
```{r}
# Calculate R squared and RMSE
RMSE100 <- round(hydroGOF::rmse(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100), digits = 6)
r2_100 <- round(rsq(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100), digits = 6)
pear_cor_100 <- cor(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100 <- cor(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100, method = "spearman")
pear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100, method = "pearson")
spear_cor_100_test <- cor.test(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100, method = "spearman")
bias100 <- round(bias(grounddat_field_gedi$rh100_a6,grounddat_field_gedi$field_height100), digits = 6)

RMSE99 <-round(hydroGOF::rmse(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99), digits = 6)
r2_99 <- round(rsq(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99), digits = 6)
pear_cor_99 <- cor(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99 <- cor(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99, method = "spearman")
pear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99, method = "pearson")
spear_cor_99_test <- cor.test(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99, method = "spearman")
bias99 <-round(bias(grounddat_field_gedi$rh99_a6,grounddat_field_gedi$field_height99), digits = 6)

RMSE98 <-round(hydroGOF::rmse(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98), digits = 6)
r2_98 <- round(rsq(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98), digits = 6)
pear_cor_98 <- cor(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98 <- cor(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98, method = "spearman")
pear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98, method = "pearson")
spear_cor_98_test <- cor.test(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98, method = "spearman")
bias98 <-round(bias(grounddat_field_gedi$rh98_a6,grounddat_field_gedi$field_height98), digits = 6)

RMSE95 <-round(hydroGOF::rmse(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95), digits = 6)
r2_95 <- round(rsq(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95), digits = 6)
pear_cor_95 <- cor(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95 <- cor(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95, method = "spearman")
pear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95, method = "pearson")
spear_cor_95_test <- cor.test(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95, method = "spearman")
bias95 <-round(bias(grounddat_field_gedi$rh95_a6,grounddat_field_gedi$field_height95), digits = 6)
```

Fancy Plot

```{r}
# gedi
dat <- read_csv("~/Desktop/Research_2022/Data/GEDI/cameroon_filtered_with_distances.csv")
# Read in field data
fielddat <- read.csv("~/Desktop/Research_2022/Data/GEDI/cameroon_field_lidar.csv")
# reserve- for crs
reserve <- readOGR('~/Desktop/Research/Cameroon/DjaFaunalReserve',"DjaFaunalReserveOSM")
# Cameroon lidar
cam_lidar <- raster("~/Desktop/Research/Cameroon/CHM_1m.tif")

# make list of shots
shot <- as.list(unique(fielddat$Shot_Number))
dat <- dat[dat$Shot_Number%in% shot, ]
shot <- as.list(unique(dat$Shot_Number))


# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs"))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)
plot(cam_buff)

hei <- as(cam_buff, "data.frame")
chm <- raster::extract(cam_lidar, cam_buff, method = "simple", df=TRUE, cellnumbers=TRUE)
summary(hei$lidar_height)
```

```{r}
# make fancy plot
i = 1
par(mfrow = c(3,5), mai=c(0,0,0,0))
for (val in shot){
  temp <- subset(dat, dat$Shot_Number == val)
  # convert GEDI data to spatial points dataframe
  cam_proj <- crs(reserve)
  coords<- temp[,c("Longitude","Latitude")]
  temp_spdf <- SpatialPointsDataFrame(coords=coords,
                                     data=temp,
                                     proj4string=cam_proj)
  temp_spdf <- spTransform(temp_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
  temp_buff <- gBuffer(temp_spdf, width= 42, byid = TRUE)
  lidar_chm_crop <- cam_lidar %>% mask(temp_buff) %>%
          crop(temp_buff)
  plot(lidar_chm_crop, 
     breaks = c(5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60), 
     col = terrain.colors(12), legend = FALSE, ylab="",yaxt="n", xlab="",xaxt="n")
  i = i+1}
plot(lidar_chm_crop, legend.only = TRUE, cex = 2)
```


```{r}
# Fancy plots
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")

# make field data into shp file
field <- subset(fielddat, fielddat$Shot_Number == "s29010100300314279")
coords<- field[,c("Longitude","Latitude")]
cam_proj <- crs(reserve)
spdf_ground <- SpatialPointsDataFrame(coords=coords,
                                   data=field,
                                   proj4string=cam_proj)
spdf_ground <- spTransform(spdf_ground, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# subset really tall tree
#tall <- subset(fielddat, fielddat$`Tree ID` == 68)
#coords<- tall[,c("Longitude","Latitude")]
#cam_proj <- crs(reserve)
#tall_spdf <- SpatialPointsDataFrame(coords=coords,
#                                   data=tall,
#                                   proj4string=cam_proj)
#tall_spdf <- spTransform(tall_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# add shapefile on top of the existing raster
plot(lidar_chm_crop)
plot(spdf_ground, add = TRUE, col = spdf_ground$Height)
plot(tall_spdf, add = TRUE, col = "white")
summary(lidar_chm_crop)
```

```{r}
# Fancy plots
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")
```

```{r}
# Make a function that creates plot when given a shot number
make_plot <- function(shot_num) {
  dat <- subset(dat, dat$Shot_Number == shot_num)
  # convert GEDI data to spatial points dataframe
  cam_proj <- crs(reserve)
  coords<- dat[,c("Longitude","Latitude")]
  cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                     data=dat,
                                     proj4string=cam_proj)
  cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
  cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)
  lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
            crop(cam_buff)
  p1<-plot(lidar_chm_crop, 
     breaks = c(10, 20, 30, 40, 50), 
     col = terrain.colors(5), legend = FALSE)
}

plot(lidar_chm_crop, 
     breaks = c(5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60), 
     col = terrain.colors(12))
```

```{r}
par(mfrow=c(3,1))
make_plot("s29010100300314279")
make_plot("s29010100300314279")
plot(lidar_chm_crop, legend.only=TRUE)
```



```{r}
dat <- subset(dat, dat$Shot_Number == "s29010100300314279")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop, main = "Cropped lidar chm")
```


```{r}
dat <- subset(dat, dat$Shot_Number == "s29010000300321833")
# convert GEDI data to spatial points dataframe
cam_proj <- crs(reserve)
coords<- dat[,c("Longitude","Latitude")]
cam_spdf <- SpatialPointsDataFrame(coords=coords,
                                   data=dat,
                                   proj4string=cam_proj)
cam_spdf <- spTransform(cam_spdf, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))
cam_buff <- gBuffer(cam_spdf, width= 21, byid = TRUE)

# cut raster data to buffer shp file
# crop the lidar raster using the vector extent
lidar_chm_crop <- cam_lidar %>% mask(cam_buff) %>%
          crop(cam_buff)
plot(lidar_chm_crop)
p1 <- plot(lidar_chm_crop, xlim = c(257097, 257099),
     ylim = c(353060, 353080), main = "Cropped lidar chm")

# make field data into shp file
field <- subset(fielddat, fielddat$Shot_Number == "s29010000300321833")
coords<- field[,c("Longitude","Latitude")]
cam_proj <- crs(reserve)
spdf_ground <- SpatialPointsDataFrame(coords=coords,
                                   data=field,
                                   proj4string=cam_proj)
spdf_ground <- spTransform(spdf_ground, CRS("+proj=utm +zone=33 +datum=WGS84 +units=m +no_defs "))

# add shapefile on top of the existing raster
plot(lidar_chm_crop)
plot(spdf_ground, add = TRUE, col = spdf_ground$Height)
plot(tall_spdf, add = TRUE, col = "white")
summary(lidar_chm_crop)
```
## Summary of Results
\begin{tabular}{|c|c|c|}
		\multicolumn{1}{r}{}
		&  \multicolumn{1}{c}{Cancer}
		& \multicolumn{1}{c}{No cancer}
		& \multicolumn{1}{c}{Total} \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
		number & number & number \\
		\cline{2-4}
\end{tabular}


